---
title: "DATS 6101: Intro to Data Science - Mid Term Project"
author: "Team 8: Dataverse"
date: "`r Sys.Date()`"
output:
  html_document:
    code_folding: hide
    number_sections: false
    toc: yes
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc: yes
    toc_depth: '3'
---


```{r , results=T}
# knitr::opts_chunk$set(warning = F, results = "markup", message = F)
knitr::opts_chunk$set(warning = F, results = "hide",message = F)
options(scientific=T, digits = 3)
```



```{r results=T}
#Loading libraries
library(ezids)
library(ggplot2)
```


```{r results=T}
car_data = data.frame(read.csv('cars.csv'))
str(car_data)
```

## Data cleaning

```{r results=T}
car_data$transmission = as.factor(car_data$transmission)
car_data$engine_fuel = as.factor(car_data$engine_fuel)
car_data$engine_has_gas = as.factor(car_data$engine_has_gas)
car_data$engine_type = as.factor(car_data$engine_type)
car_data$body_type = as.factor(car_data$body_type)
car_data$has_warranty = as.factor(car_data$has_warranty)
car_data$state = as.factor(car_data$state)
car_data$drivetrain = as.factor(car_data$drivetrain)
car_data$is_exchangeable = as.factor(car_data$is_exchangeable)
car_data$location_region = as.factor(car_data$location_region)
```

Updating the feature as factor to make them categorical


```{r results=T}
#car_data$year_produced <- strptime(car_data$year_produced, "%Y")
```



```{r results=T}
feature_cols <- c(20:29)
car_data[feature_cols] <- lapply(car_data[feature_cols],factor)
str(car_data)
```

Updating the unknown features as factor in bulk


Dropping columns which are not relevant

```{r results=T}
car_data <- subset(car_data, select = -c(model_name,engine_has_gas,state,location_region))
```

checking NA values

```{r results=T}
sapply(car_data, function(x) sum(is.na(x)))
```

Getting some null values in engine capacity

```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- mean(car_data$engine_capacity,na.rm = TRUE)
sapply(car_data, function(x) sum(is.na(x)))
```

Replaced 10 missing values for engline capacity with mean of rest of the values

```{r results=T}
# car_data = outlierKD2(car_data, odometer_value, TRUE, TRUE, TRUE, TRUE)
# odometer_value_na = sum(is.na(car_data$odometer_value))
# print(odometer_value_na)
```

There might be the possibility that vehicle is used for longer time

## Exploratory data analysis

```{r results=T}
p <- ggplot(car_data, aes(x = price_usd)) +
     geom_histogram(aes(y = stat(density), colour = "HIST"), fill="light blue", bins=30, alpha=.5) +
      labs(x = 'price(In USD)') + labs(title = 'Distribution of resale prices - Histogram')
p
```

## Price destribution

Transmission feature
```{r results=T}
plot1 <- ggplot(car_data, aes(x=transmission, y=price_usd)) + 
  geom_boxplot(color="black", fill="orange")+
  labs(x="car_transmission",y="price_usd") + labs(title="boxplot - Car Price distribution based on transmission type") 
plot1
```


## odometer_value

```{r results=T}
ggplot(data = car_data) +
    geom_smooth(mapping = aes(x = odometer_value, y = price_usd)) +
    scale_x_continuous(name="odometer_value", labels = scales::comma) +
        labs(x = 'odometer_value', y = 'price(in USD)') + labs(title = 'line plot - prices vs odometer values')
```


We can clearly see that as odometer value is increasing, car prices are going down.

```{r results=T}
plot3 <- ggplot(car_data,aes(x = odometer_value,y = '',color = odometer_value)) +
        geom_violin(color="black", fill="pink") + geom_boxplot(width = .2,color="black", fill="violet") +
        labs(x = 'odometer_value') + labs(title = 'Violin plot + box plot for odameter values')
plot3
```


violin plot, checking odometer distribution and box plot in the same graph. 


Scatter plot with fitting line


```{r}
plot(car_data$odometer_value, car_data$price_usd) 
```

```{r}
updated_data = outlierKD2(car_data, odometer_value, TRUE, TRUE, TRUE, TRUE)
```

```{r}
ggplot(updated_data, aes(x=odometer_value, y=price_usd)) +
   geom_point()+
   geom_smooth(method=lm) +
   labs(title = 'scatter plot - car prices vs odometer values') +
   labs(x = 'odometer values(in KM)', y = 'price(in USD)') + scale_x_continuous(name='odometer values(in KM)', labels = scales::comma)
```

By removing outliers from odometer value, we are getting good relation for price vs odometer value.

## year_produced

```{r results=T}
ggplot(data = car_data) +
    geom_smooth(color = 'red',mapping = aes(x = year_produced, y = price_usd)) + labs(x = 'Year of production', y = 'Price(in USD)') + 
    labs(title ='Year wise car price values')
```


As we can see that car prices of vintage cars is high. Also the resell price is high for latest cars.

```{r results=T}
plot_transmission <- ggplot(data = car_data) +
    geom_smooth(color = 'red',mapping = aes(x = year_produced, y = price_usd,linetype = transmission)) + 
    labs(title = 'Year wise car price values based on transmission type') + labs(x = 'Year of production', y = 'Price(in USD)')
plot_transmission
```

To check the Vintage category, mechanical are categorize as vintage and automatic cars are available from 1978. We are getting the similar results compared to the previous plot based on complete data.

## Engine fuel

```{r results=T}
plot1 <- ggplot(car_data, aes(x=engine_fuel, y=price_usd)) + 
  geom_boxplot(color="black", fill="green")+
  labs(x="engine_fuel",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on engine_fuel") 
plot1
```


## car prices based on engine type

```{r results=T}
library(ggpubr)
xplot <- ggdensity(car_data, "price_usd", fill = "engine_type",
                   palette = "arc") + labs(title = 'density plot for car price based on engine type category') + labs(x = 'price(in USD)')
xplot
```

We can clearly separate out electric engine category from diesel and gasoline. most of the distribution is overlapped for diesel and gasoline and we can see the Pareto distribution in both the categories.
## engine capacity

```{r results=T}
ggplot(data = car_data, aes(x = engine_capacity, y = price_usd)) +
    geom_smooth(color = 'yellow') +
    labs(title = 'Car price values based on Engine Capacity') + labs(x = 'Engine capacity', y = 'price(in USD)')
```


As engine capacity is going high, the prices are also increasing.

## has warranty feature
```{r results=T}
plot_warranty <- ggplot(car_data, aes(x=has_warranty, y=price_usd)) + 
  geom_boxplot(color="black", fill="violet")+
  labs(x="has_warranty",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on car is in warranty or not") 
plot_warranty
```

As we can see, cars which are in warranty have the better resell prices than the cars which are not covered under warranty.
Also we can see so many outliers in 'no warranty' categories. That pool is belongs to the vintage cars where prices are high but the car is not in the warranty.

## body type feature
```{r results=T}
plot_body <- ggplot(car_data, aes(x=body_type, y=price_usd)) + 
  geom_boxplot(color="black", fill="#F48FB1")+
  labs(x="body type",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on body type") 
plot_body
```

## car manufacturer

```{r results=T}
df_new <- aggregate( price_usd ~ manufacturer_name, car_data, median )
df_new
```

```{r}
top_10_costy_brands <- df_new[df_new$price_usd %in% tail(sort(df_new$price_usd),10),]
top_10_costy_brands
```

```{r}
top_10_manufactuerer_avg_price=subset(car_data,manufacturer_name=='Acura'|manufacturer_name=="Buick"|manufacturer_name=="cadillac"|manufacturer_name=="Infiniti"|manufacturer_name=="Jaguar"|manufacturer_name=="Land Rover"| manufacturer_name=='Lexus'| manufacturer_name=="Mini"|manufacturer_name=="Porsche"|manufacturer_name=="Skoda")
top_10_manufactuerer_avg_price
```

```{r results=T}
plot_body <- ggplot(top_10_manufactuerer_avg_price, aes(x=manufacturer_name, y=price_usd)) + 
  geom_boxplot(color="black", fill="Yellow")+
  labs(x="Car_Manufacturer",y="Price(in USD)") + labs(title=" Top 10 Manufacturers and its Car Price") 
plot_body
```

## Car color

```{r results=T}
plot1 <- ggplot(car_data, aes(x=color, y=price_usd)) + 
  geom_boxplot(color="blue", fill="orange")+
  labs(x="Car Color",y="price_usd") + labs(title="Boxplot - Car Color and its Price (In USD)") 
plot1
```

## has warranty feature

```{r results=T}
plot_warranty <- ggplot(car_data, aes(x=has_warranty, y=price_usd)) + 
  geom_boxplot(color="black", fill="violet")+
  labs(x="has_warranty",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on car is in warranty or not") 
plot_warranty
```

As we can see, cars which are in warranty have the better resell prices than the cars which are not covered under warranty.
Also we can see so many outliers in 'no warranty' categories. That pool is belongs to the vintage cars where prices are high but the car is not in the warranty.

## Number of upgrades

```{r result=T}
plot_upgrade <- ggplot(car_data, aes(x=up_counter, y=price_usd)) + 
  geom_smooth(color="black", fill="#F48FB1")+
  labs(x="No of Upgrades",y="price_usd") + labs(title="No of upgrades vs Price_usd") 
plot_upgrade
 
```

Certain number of upgrades are actually impacting the car price but the resale price is going down after so many upgrades.

## body Type

```{r results=T}
plot_body <- ggplot(car_data, aes(x=body_type, y=price_usd)) + 
  geom_boxplot(color="black", fill="#F48FB1")+
  labs(x="body type",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on body type") 
plot_body
```

#Number of photos

Creating buckets for number of photos feature

```{r}

Photo_bucket <- within(car_data, {   
  Photo_bucket.cat <- NA # need to initialize variable
  Photo_bucket.cat[number_of_photos < 6] <- "0-5"
  Photo_bucket.cat[number_of_photos >= 6 & number_of_photos < 11] <- "6-10"
  Photo_bucket.cat[number_of_photos >= 11 & number_of_photos < 16] <- "11-15"
  Photo_bucket.cat[number_of_photos >= 16 & number_of_photos < 21] <- "16-20"
  Photo_bucket.cat[number_of_photos >= 21 & number_of_photos < 26] <- "21-25"
  Photo_bucket.cat[number_of_photos >= 26 & number_of_photos < 31] <- "26-30"
  Photo_bucket.cat[number_of_photos > 30] <- "more than 30"
   } )

#str(dat)


Photo_bucket$Photo_bucket.cat <- factor(Photo_bucket$Photo_bucket.cat, levels= c("0-5","6-10","11-15","16-20","21-25","26-30","more than 30"))

```

```{r}

ggplot(Photo_bucket, aes(y = price_usd , x = Photo_bucket.cat)) + geom_boxplot(color="black", fill="#bc5090") + labs(title = 'Boxplot - impact of number of photos on car prices') + labs(x = 'Number of photos', y = 'Price(in USD)')

```


## Drivetrain

```{r results=T}
plot_warranty <- ggplot(car_data, aes(x=drivetrain, y=price_usd)) + 
  geom_boxplot(color="black", fill="#AF7AC5")+
  labs(x="drivetrain",y="price_usd") + labs(title="boxplot - Car Price distribution based on car drivetrain") 
plot_warranty
```

Car prices are high in case of all wheel drive and for front and rear wheel drive, the median price range is almost same.


## Duration listed

relation of resale prices with duration listed on the catalog

```{r results=T}
ggplot(data = car_data, aes(x = duration_listed, y = price_usd)) +
    geom_smooth(color = '#AF7AC5') + 
    labs(title = 'Car prices based on duration listed') + labs(x="Duration listed",y="Price(in USD)")
```
