---
title: "Hypothesis_testing"
author: "Team Dataverse(Yashwant, Manoj, Sai and Sravya)"
date: "2022-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r results=T}
#Loading libraries
library(ezids)
library(ggplot2)
library(corrplot)
library(tidyverse)
```



```{r}
car_data = data.frame(read.csv('cars.csv'))
str(car_data)
```

## Data cleaning

```{r results=T}
car_data$transmission = as.factor(car_data$transmission)
car_data$engine_fuel = as.factor(car_data$engine_fuel)
car_data$engine_has_gas = as.factor(car_data$engine_has_gas)
car_data$engine_type = as.factor(car_data$engine_type)
car_data$body_type = as.factor(car_data$body_type)
car_data$has_warranty = as.factor(car_data$has_warranty)
car_data$state = as.factor(car_data$state)
car_data$drivetrain = as.factor(car_data$drivetrain)
car_data$is_exchangeable = as.factor(car_data$is_exchangeable)
car_data$location_region = as.factor(car_data$location_region)
```


```{r results=T}
feature_cols <- c(20:29)
car_data[feature_cols] <- lapply(car_data[feature_cols],factor)
str(car_data)
```

```{r results=T}
sapply(car_data, function(x) sum(is.na(x)))
```


```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- 0
mean(car_data$engine_capacity)
median(car_data$engine_capacity)
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
s <- getmode(car_data$engine_capacity)
s
```

```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- mean(car_data$engine_capacity,na.rm = TRUE)
sapply(car_data, function(x) sum(is.na(x)))
```

## Unknown features(feature0 to feature9)

### Feature 0

Is feature_0 impacting the average car price?

```{r}
with_feature_0<-subset(car_data,feature_0 == 'True')
without_feature_0<-subset(car_data,feature_0 == 'False')
```

```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature0 = t.test(x=with_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature0


Hypothesis_test_price_without_feature0 = t.test(x=without_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature0
```

We got low price interval if feature0 is in the car. So probably its outdated feature.

### Feature 1

Is feature_1 impacting the average car price?

```{r}
with_feature_1<-subset(car_data,feature_1 == 'True')
without_feature_1<-subset(car_data,feature_1 == 'False')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature1 = t.test(x=with_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature1


Hypothesis_test_price_without_feature1 = t.test(x=without_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature1
```

We got low price interval if feature0 is in the car.

### Feature 2

Is feature_2 impacting the average car price?

```{r}
with_feature_2<-subset(car_data,feature_2 == 'True')
without_feature_2<-subset(car_data,feature_2 == 'False')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature2 = t.test(x=with_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature2


Hypothesis_test_price_without_feature2 = t.test(x=without_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature2
```

### Feature_3

```{r}
with_feature_3<-subset(car_data,feature_3 == 'True')
without_feature_3<-subset(car_data,feature_3 == 'False')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature3 = t.test(x=with_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature3


Hypothesis_test_price_without_feature3 = t.test(x=without_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature3
```

### Feature_4

```{r}
with_feature_4<-subset(car_data,feature_4 == 'True')
without_feature_4<-subset(car_data,feature_4 == 'False')
```

```{r results=T}

mean_price = mean(car_data$price_usd) 
mean_price


Hypothesis_test_price_with_feature4 = t.test(x=with_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature4


Hypothesis_test_price_without_feature4 = t.test(x=without_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature4
```

### Feature_5

```{r}
with_feature_5<-subset(car_data,feature_5 == 'True')
without_feature_5<-subset(car_data,feature_5 == 'False')
```


```{r results=T}

mean_price = mean(car_data$price_usd) 
mean_price


Hypothesis_test_price_with_feature5 = t.test(x=with_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature5


Hypothesis_test_price_without_feature5 = t.test(x=without_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature5
```

### Feature_6

```{r}
with_feature_6<-subset(car_data,feature_6 == 'True')
without_feature_6<-subset(car_data,feature_6 == 'False')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature6 = t.test(x=with_feature_6$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature6


Hypothesis_test_price_without_feature6 = t.test(x=without_feature_6$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature6
```

### Feature_7

```{r}
with_feature_7<-subset(car_data,feature_7 == 'True')
without_feature_7<-subset(car_data,feature_7 == 'False')
```


```{r results=T}
mean_price = mean(car_data$price_usd) 
mean_price

Hypothesis_test_price_with_feature7 = t.test(x=with_feature_7$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_with_feature7


Hypothesis_test_price_without_feature7 = t.test(x=without_feature_7$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_without_feature7
```

###feature-8

```{r}
with_feature_8<-subset(car_data,feature_8 == 'True')
without_feature_8<-subset(car_data,feature_8 == 'False')
```

```{r results=T}
mean_price = mean(car_data$price_usd) 
mean_price

Hypothesis_test_price_with_feature8 = t.test(x=with_feature_8$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_with_feature8


Hypothesis_test_price_without_feature8 = t.test(x=without_feature_8$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_without_feature8
```

###feature-9

```{r}
with_feature_9<-subset(car_data,feature_9 == 'True')
without_feature_9<-subset(car_data,feature_9 == 'False')
```

```{r results=T}
mean_price = mean(car_data$price_usd) 
mean_price

Hypothesis_test_price_with_feature9 = t.test(x=with_feature_9$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_with_feature9


Hypothesis_test_price_without_feature9 = t.test(x=without_feature_9$price_usd,mu = mean_price ,conf.level = 0.95)
#default conf.level = 0.95
Hypothesis_test_price_without_feature9
```

## Anova test on car brands

All car brands have same average car price or not?
```{r}
price_aov<-aov(price_usd ~ manufacturer_name, data=car_data)
price_aov
```

```{r}
xkabledply(price_aov, title = 'Anova test result impact of manufacturer_name on car price')
```

In this test, we are checking that is there any significant difference in the mean price on the basis of car manufacturer.
H0: there is no difference in the mean prices of the cars based on manufacturer
H1: there is a difference in the mean prices of the cars based on manufacturer

If p≤α, reject H0; otherwise, do not reject H0.

As we got p value less than α hence we reject the null hypothesis.
It means there is a significant difference in the mean price based on manufacturer.

## Warranty

is there any impact of warranty of a car on the resale price?

```{r}
with_warranty<-subset(car_data,has_warranty == 'True')
without_warranty<-subset(car_data,has_warranty == 'False')
```


```{r results = T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_warranty = t.test(x=with_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_warranty


Hypothesis_test_price_without_warranty = t.test(x=without_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_warranty
```


as we can see that mean price of the whole car dataset is not falling under the time interval we got after separating the data based on warranty feature.
Also there is significant difference in the mean car price as we got price intervals which are not overlapping.

## Chi square test of independence on Year of manufacture and price

Car resale prices are dependent on the year of manufacture?

```{r}
p_usd.intrv = cut(car_data$price_usd, c(0,10000,20000,30000,40000,50000))
year.intrv = cut(car_data$year_produced, c(1940,1950,1960,1970,1980,1990,2000,2010,2020))
lists <- list(price_intvl = as.character(p_usd.intrv),yr_interval = as.character(year.intrv))
df <- as.data.frame(do.call(cbind, lists))
conTable = table(df)
print(conTable)
```

```{r}
head(df,3)
```

```{r results=T}
chitest = chisq.test(conTable)
chitest
```

With the chi square test of independence, we are checking that resale car prices are dependent on the year of manufacture or not.
H0: Car prices and year of production are independent of each other.
H1: Car prices and year of production are dependent of each other.

If p≤α, reject H0; otherwise, do not reject H0.

as we got p value less than 0.05 hance we are rejecting the null hypothesis.

It means prices and year of production are dependent of each other


## corrplot


Correlation plot between the numerical features is considered

```{r include=FALSE}
car_data %>% select_if(is.numeric)->cars_numerical
```

```{r cor}
corrplot(cor(cars_numerical), method = 'number')
```

The above correlation plot shows the relation between all the numerical features and the price_usd.
Here, odometer_value has negative correlation with price(cc=-0.42). Year of production is highly correlated among the others and the least correlated one is up_counter and duration_listed.

ANOVA is helpful for testing three or more variables.It is similar to multiple two-sample t-tests.The one-way ANOVA is used to determine whether there are any statistically significant differences between the means of three or more independent (unrelated) groups.

One way Anova test for color and body type is performed

Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all color groups
Null Hypothesis         H0 : all means are equal
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

## Anova test for car color

```{r}
df_aov_1 = aov(price_usd ~  color , car_data)
summary(df_aov_1)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of color is different from each other.


Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of car body type
Null Hypothesis         H0 : all means are equal
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

## Anova test for body type

```{r}
df_aov_4 = aov(price_usd ~  body_type , car_data)
summary(df_aov_4)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of body type is different from each other.

## Testing engine_fuel type an engine_type

In order to showcase the one-way ANOVA hypothesis test we examine the mean resale prices of cars, grouped by their engine fuel type. To make it clear, in this example the classification/grouping is done by one variable, the major variable, the so-called factor, thus we are conducting a one-way ANOVA. In this exercise we want to test if the mean annual resale price of cars is different for different engine fuel types.
In the same way, one way anova test is performed on the engine type.

Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of engine fuel types.
Null Hypothesis         H0 : μ1=μ2=μ3=μ4=μ5=μ6
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

```{r}
df_aov_2 = aov(price_usd~  engine_fuel , car_data)
summary(df_aov_2)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine fuel type is different from each other.


Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of engine types.
Null Hypothesis         H0 : μ1=μ2=μ3
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
Significance level is alpha=0.05

```{r}
df_aov_3 = aov(price_usd~  engine_type , car_data)
summary(df_aov_3)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine type is different from each other.

## t-test for transmission type as there are only two sub groups

```{r T test, echo=TRUE}
summary(car_data$transmission)
t_auto = subset(car_data, transmission == "automatic")
t_mechanical = subset(car_data, transmission == "mechanical")
t.test(x = t_auto$price_usd, y = t_mechanical$price_usd, conf.level = 0.99)
```

## Anova test on car brands

All car brands have same average car price or not?
```{r}
price_aov<-aov(price_usd ~ manufacturer_name, data=car_data)
price_aov
```

```{r}
xkabledply(price_aov, title = 'Anova test result impact of manufacturer_name on car price')
```

As we have 55 car brands, Running the test on all car brands to check if there is any significant difference in mean car price based on manufacturer.

H0: there is no difference in the mean prices based on car brands.
H1: there is a significant difference in the mean prices based on car brands.

As we got p value less than 0.05, we will reject the null hypothesis.
It means there is a significant difference based in the mean car prices based on manufacturer 


## Anova test on top 10 car brands


```{r}
car_data_top_10 <- car_data[car_data$manufacturer_name %in% c("Acura","Buick","Cadillac","Infiniti","Jaguar","Land Rover","Lexus","Mini","Porsche","Skoda"),]
nrow(car_data_top_10)
```

```{r}
price_aov<-aov(price_usd ~ manufacturer_name, data=car_data_top_10)
price_aov
xkabledply(price_aov, title = 'Anova test result impact of top 10 manufacturer_name on car price')
```

## Anova test on Drivetrain

Is there any change in the resale price based on drive train feature? 

```{r results=T}
cartrain_aov<-aov(price_usd ~ drivetrain, data=car_data)
cartrain_aov
```

```{r}
xkabledply(cartrain_aov, title = 'Anova test result impact of drivetrain on car prices')
```

