---
title: "Hypothesis_testing"
author: "Team Dataverse(Yashwant, Manoj, Sai and Sravya)"
date: "2022-10-28"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r results=T}
#Loading libraries
library(ezids)
library(ggplot2)
```



```{r}
car_data = data.frame(read.csv('cars.csv'))
str(car_data)
```

Data cleaning

```{r results=T}
car_data$transmission = as.factor(car_data$transmission)
car_data$engine_fuel = as.factor(car_data$engine_fuel)
car_data$engine_has_gas = as.factor(car_data$engine_has_gas)
car_data$engine_type = as.factor(car_data$engine_type)
car_data$body_type = as.factor(car_data$body_type)
car_data$has_warranty = as.factor(car_data$has_warranty)
car_data$state = as.factor(car_data$state)
car_data$drivetrain = as.factor(car_data$drivetrain)
car_data$is_exchangeable = as.factor(car_data$is_exchangeable)
car_data$location_region = as.factor(car_data$location_region)
```



```{r results=T}
#car_data$year_produced <- strptime(car_data$year_produced, "%Y")
```

```{r results=T}
feature_cols <- c(20:29)
car_data[feature_cols] <- lapply(car_data[feature_cols],factor)
str(car_data)
```

```{r results=T}
sapply(car_data, function(x) sum(is.na(x)))
```


```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- 0
mean(car_data$engine_capacity)
median(car_data$engine_capacity)
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
s <- getmode(car_data$engine_capacity)
s
```

```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- mean(car_data$engine_capacity,na.rm = TRUE)
sapply(car_data, function(x) sum(is.na(x)))
```

## Unknown features(feature0 to feature9)

Is feature_0 impacting the average car price?

```{r}
with_feature_0<-subset(car_data,feature_0 == 'True')
without_feature_0<-subset(car_data,feature_0 == 'False')
```

```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature0 = t.test(x=with_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature0


Hypothesis_test_price_without_feature0 = t.test(x=without_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature0
```

Is feature_1 impacting the average car price?

```{r}
with_feature_1<-subset(car_data,feature_1 == 'True')
without_feature_1<-subset(car_data,feature_1 == 'False')
```


```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature1 = t.test(x=with_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature1


Hypothesis_test_price_without_feature1 = t.test(x=without_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature1
```

Is feature_2 impacting the average car price?

```{r}
with_feature_2<-subset(car_data,feature_2 == 'True')
without_feature_2<-subset(car_data,feature_2 == 'False')
```


```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature2 = t.test(x=with_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature2


Hypothesis_test_price_without_feature2 = t.test(x=without_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature2
```
```{r}
with_feature_3<-subset(car_data,feature_3 == 'True')
without_feature_3<-subset(car_data,feature_3 == 'False')
```


```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature3 = t.test(x=with_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature3


Hypothesis_test_price_without_feature3 = t.test(x=without_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature3
```

```{r}
with_feature_4<-subset(car_data,feature_4 == 'True')
without_feature_4<-subset(car_data,feature_4 == 'False')
```

```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature4 = t.test(x=with_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature4


Hypothesis_test_price_without_feature4 = t.test(x=without_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature4
```

```{r}
with_feature_5<-subset(car_data,feature_5 == 'True')
without_feature_5<-subset(car_data,feature_5 == 'False')
```


```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature5 = t.test(x=with_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature5


Hypothesis_test_price_without_feature5 = t.test(x=without_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature5
```

```{r}
with_feature_6<-subset(car_data,feature_6 == 'True')
without_feature_6<-subset(car_data,feature_6 == 'False')
```


```{r results=T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_feature6 = t.test(x=with_feature_6$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature6


Hypothesis_test_price_without_feature6 = t.test(x=without_feature_6$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature6
```

## Anova test on car brands

All car brands have same average car price or not?
```{r}
price_aov<-aov(price_usd ~ manufacturer_name, data=car_data)
price_aov
```

```{r}
xkabledply(price_aov, title = 'Anova test result impact of manufacturer_name on car price')
```



## Warranty

is there any impact of warranty of a car on the resale price?

```{r}
with_warranty<-subset(car_data,has_warranty == 'True')
without_warranty<-subset(car_data,has_warranty == 'False')
```


```{r results = T}
#mean of GRE score
mean_price = mean(car_data$price_usd) #Mean GRE based on full data
mean_price
#for GRE score of admitted students 

Hypothesis_test_price_with_warranty = t.test(x=with_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_warranty


Hypothesis_test_price_without_warranty = t.test(x=without_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_warranty
```


## Chi square test of independence on Year of manufacture and price

Car resale prices are dependent on the year of manufacture?

```{r}
p_usd.intrv = cut(car_data$price_usd, c(0,10000,20000,30000,40000,50000))
year.intrv = cut(car_data$year_produced, c(1940,1950,1960,1970,1980,1990,2000,2010,2020))
lists <- list(price_intvl = as.character(p_usd.intrv),yr_interval = as.character(year.intrv))
df <- as.data.frame(do.call(cbind, lists))
conTable = table(df)
print(conTable)
```

```{r}
df
```

```{r results=T}
chitest = chisq.test(conTable)
chitest
```

Correlation plot between the numerical features is considered

```{r include=FALSE}
library(corrplot)
library(tidyverse)

car_data %>% select_if(is.numeric)->cars_numerical
```

```{r cor}
corrplot(cor(cars_numerical), method = 'number')
```

The above correlation plot shows the relation between all the numerical features and the price_usd.
Here, odometer_value has negative correlation with price(cc=-0.42). Year of production is highly correlated among the others and the least correlated one is up_counter and duration_listed.

ANOVA is helpful for testing three or more variables.It is similar to multiple two-sample t-tests.The one-way ANOVA is used to determine whether there are any statistically significant differences between the means of three or more independent (unrelated) groups.

One way Anova test for color and body type is performed

Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all color groups
Null Hypothesis         H0 : all means are equal
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

```{r}
df_aov_1 = aov(price_usd ~  color , car_data)
summary(df_aov_1)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of color is different from each other.


Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of car body type
Null Hypothesis         H0 : all means are equal
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

```{r}
df_aov_4 = aov(price_usd ~  body_type , car_data)
summary(df_aov_4)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of body type is different from each other.

Testing engine_fuel type an engine_type

In order to showcase the one-way ANOVA hypothesis test we examine the mean resale prices of cars, grouped by their engine fuel type. To make it clear, in this example the classification/grouping is done by one variable, the major variable, the so-called factor, thus we are conducting a one-way ANOVA. In this exercise we want to test if the mean annual resale price of cars is different for different engine fuel types.
In the same way, one way anova test is performed on the engine type.

Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of engine fuel types.
Null Hypothesis         H0 : μ1=μ2=μ3=μ4=μ5=μ6
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

```{r}
df_aov_2 = aov(price_usd~  engine_fuel , car_data)
summary(df_aov_2)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.
Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine fuel type is different from each other.


Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of engine types.
Null Hypothesis         H0 : μ1=μ2=μ3
Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
Significance level is alpha=0.05

```{r}
df_aov_3 = aov(price_usd~  engine_type , car_data)
summary(df_aov_3)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine type is different from each other.

t-test for transmission type as there are only two sub groups

```{r T test, echo=TRUE}
summary(car_data$transmission)
t_auto = subset(car_data, transmission == "automatic")
t_mechanical = subset(car_data, transmission == "mechanical")
t.test(x = t_auto$price_usd, y = t_mechanical$price_usd, conf.level = 0.99)
```

