---
title: "Used Car Price Prediction - Mid Term Summary Paper"
author: "Team Dataverse"
date: "`r Sys.Date()`"
# date: "`r Sys.Date()`"
output:
  rmdformats::readthedown:
    code_folding: hide
    highlight: pygments
---

<style type="text/css">
p{ /* Normal  */
   font-size: 18px;
}
body{ /* Normal  */
   font-size: 18px;
}
td {  /* Table  */
   font-size: 14px;
}
h1 { /* Header 1 */
 font-size: 32px;
}
h2 { /* Header 2 */
 font-size: 26px;
}
h3 { /* Header 3 */
 font-size: 22px;
}
code.r{ /* Code block */
  font-size: 14px;
}
pre { /* Code block */
  font-size: 14px
}
</style>
---


```{r init, include=FALSE}
# some of common options (and the defaults) are: 
# include=T, eval=T, echo=T, results='hide'/'asis'/'markup',..., collapse=F, warning=T, message=T, error=T, cache=T, fig.width=6, fig.height=4, fig.dim=c(6,4) #inches, fig.align='left'/'center','right', 
library(ezids)
knitr::opts_chunk$set(warning = F, results = "markup", message = F, comment = NA)
# knitr::opts_chunk$set(warning = F, results = "hide", message = F)
options(scientific=T, digits = 3) 
# options(scipen=9, digits = 3) 
# ‘scipen’: integer. A penalty to be applied when deciding to print numeric values in fixed or exponential notation.  Positive values bias towards fixed and negative towards scientific notation: fixed notation will be preferred unless it is more than ‘scipen’ digits wider.
# use scipen=999 to prevent scientific notation at all times
```

## Why Used Car Price Prediction?
A microchip shortage caused by the COVID-19 pandemic has had a significant impact on the global automobile industry, raising used car prices for buyers.

Automobile manufacturers are unable to produce new vehicles due to raw material supply chain issues. Due to a lower-than-usual supply of vehicles on their lots, dealers selling new cars have struggled to keep up with demand. This has an impact on used car dealerships, who are charging higher prices to sell their vehicles. Customers who want to sell their vehicle to a used car dealership, on the other hand, will benefit from higher trade-in values.

Price variations are common and can lead to misleading prices on any other website, necessitating the development of a tool to predict the pricing of used cars based on real data gathered from local websites in order to provide consumers with an accurate evaluation of cars.

When Team Dataverse learned about the recent issue that arose in the automobile industry as a result of the COVID global pandemic, we attempted to determine which car attributes are most important in determining the price of a used car. Our analysis will be accurate enough to assist consumers in determining car pricing for either selling or purchasing purposes based on the vehicle's features.


## Prior Research and Analysis
With the rise of individual cars, more people are looking into getting their own car at an affordable price, usually looking in the used car market, "For each and every new car sold in the UAE in 2019, about 3.5 used cars were sold" (BIELSKI & RAMARATHNAM, 2020). In the coming years, the industry will be revolutionized, with markets powered by digitalization and new business models to improve focus efficiency and consumer needs.

In recent years, used car prices have risen. Prices increased by 4-10% between 2018 and 2020, but dealers sold more cars in a shorter period of time. Furthermore, analysts have shown that car depreciation costs have only been decreasing in the UAE, a previously unseen phenomenon that has led to an increase in second-hand car demand (Bridge, 2020).

Manheim The used vehicle index has seen an unprecedented increase in used car value, increasing 6.81% in the first 15 days of April 2021 compared to the month of March. In addition, the value has increased by 52.2% since April 2020, with the latest trend indicators indicating a few more weeks of appreciation. This is due to stimulus payments and tax refunds as a result of the Covid-19 ramifications, as well as a global decrease in car production. (2021 Used Vehicle Value Index).


## About the Dataset

The Used-Cars-Catalog data set was obtained from Kaggle (the World's Largest Data Scientists Community) in order to investigate the used car market. Data is pulled in Belarus (western Europe) on December 2, 2019. 

**Dataset Link:**
https://www.kaggle.com/datasets/lepchenkov/usedcarscatalog?selectcars.csv=

•	The dataset contains 38531 observations.

•	The dataset contains 30 variables.

**Dataset Variables:**

•	[1-5] Manufacturer Name, Model Name, Transmission, Color, Odometer Value

•	[6-10] Year Produced, Engine Fuel, Engine Has Gas, Engine Type, Engine Capacity

•	[11-15] Body Type, Warranty, State, Drivetrain, Price in USD

•	[16-20] Is Exchangeable, Location, Number of Photos, Upgrade Count, Duration Listed 

•	[21-30] Feature 0 to Feature 9

•	The engine capacity variable has ten null values that have been replaced by the mean because they have no effect on the data distribution.

•	Our team used exploratory data analysis and hypothesis testing to estimate the relationship between the dependent variable (Car's price), and several independent variables that included both numerical and categorical values.

## Limitations of Dataset
•  We have the data only till 2019. So, we don’t know the post covid trends and the changes in the prices couldn’t be explained.

•  The dataset has data only related to the Belarus region. There is no global exposure.

•  More data can lead to predictions that are more reliable. 

•  Second, there might be additional traits that are reliable predictors. 

•  Here are some examples of variables that could enhance the model: doors, gas mileage (mpg), time spent undergoing mechanical and cosmetic repairs, used-to-new ratio, and appraisal-to-trade ratio.

• There are ten unknown features (0-9) in the dataset. We don't know which part of the car these unknown features represent. Based on the results, we can conclude whether the feature is outdated or a luxury car feature.

## SMART Questions

**Why team came up with the below smart Questions?**

Data Verse team members are avid vehicle enthusiasts, therefore we used their knowledge of the most prevalent and crucial aspects to come up with SMART questions. In order to arrive at a conclusion on the target variable price, a few questions were posed, and analysis was conducted utilizing Boxplots, Scatterplots, t-tests, anova, and chi-square tests, among other tools.


**What are the factors affecting the prices of used cars?**

1)	Is the warranty impacting the resale value of the cars?

2)	Does the odometer value have any impact on the car prices?

3)	Are the car prices dependent on the manufacturer or year of production?

4)	Does colour and body type have any impact on the resale prices of the cars?

5)	Does the number of photos have any impact on the car’s resale value?

6)	Does drivetrain have any impact on the car’s resale value?

7)	Are the resale prices of the cars dependent on fuel and engine type?

8)	Are the prices of the cars different based on the transmission type and engine capacity?

9)	Does unknown features have any impact on car prices?


## Importing the Libraries and Dataset

```{r Importing Libraries, include=FALSE}
# Required libraries are installed
library(ezids)
library(plotly)
library(viridis)
library(hrbrthemes)
library(ggplot2)
library(corrplot)
library(tidyverse)
```

We have imported the data from cars.csv file and stored it as car_data dataframe.

```{r results=T}
car_data = data.frame(read.csv('cars.csv'))
str(car_data)
```

## Data cleaning

Convert the below variables in the dataset as factor to make them categorical.

•	transmission

•	engine_fuel

•	engine_has_gas

•	engine_type

•	body_type

•	has_warranty

•	state

•	drivetrain

•	is exchangeable

```{r results=T}
car_data$transmission = as.factor(car_data$transmission)
car_data$engine_fuel = as.factor(car_data$engine_fuel)
car_data$engine_has_gas = as.factor(car_data$engine_has_gas)
car_data$engine_type = as.factor(car_data$engine_type)
car_data$body_type = as.factor(car_data$body_type)
car_data$has_warranty = as.factor(car_data$has_warranty)
car_data$state = as.factor(car_data$state)
car_data$drivetrain = as.factor(car_data$drivetrain)
car_data$is_exchangeable = as.factor(car_data$is_exchangeable)
car_data$location_region = as.factor(car_data$location_region)
```

Updating the unknown features (Feature 0 to Feature 9) as factor in bulk

```{r results=T}
feature_cols <- c(20:29)
car_data[feature_cols] <- lapply(car_data[feature_cols],factor)
str(car_data)
```

In the dataset, there are 10 null values present in engine_capacity variable.

```{r results=T}
sapply(car_data, function(x) sum(is.na(x)))
```

```{r}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- 0
getmode <- function(v) {
   uniqv <- unique(v)
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
s <- getmode(car_data$engine_capacity)
cat("For Engine Capcity Mean is:",mean(car_data$engine_capacity),"Median is:",median(car_data$engine_capacity),"Mode is:",s)
```

•	The engine capacity variable has 10 null values which have been replaced by the mean as it will not impact the distribution of data.


```{r results=T}
car_data$engine_capacity[is.na(car_data$engine_capacity)] <- mean(car_data$engine_capacity,na.rm = TRUE)
sapply(car_data, function(x) sum(is.na(x)))
```


•	We are not removing the outilers in the odometer variable as some of the vehicles might be in use from longer time.

•	The team examined all variables except model_name, engine_has_gas, car_state, Location_region, and Duration List.


## Exploratory Data Analysis

This graph shows about the distribution of Resale prices of the entire dataset.

```{r results=T}
p <- ggplot(car_data, aes(x = price_usd)) +
     geom_histogram(aes(y = stat(density), colour = "HIST"), fill="light blue", bins=30, alpha=.5) +
      labs(x = 'price(In USD)') + labs(title = 'Distribution of Resale Prices - Histogram')
p
```

## Is the warranty impacting the resale value of the cars?
  
**Boxplot: Price(In USD) vs has_warranty**

  ```{r results=T}
plot_warranty <- ggplot(car_data, aes(x=has_warranty, y=price_usd)) + 
  geom_boxplot(color="black", fill="violet")+
  labs(x="has_warranty",y="price(in USD)") + labs(title="Boxplot - Car Price distribution based on car is in warranty or not") 
plot_warranty
```

As we can see, cars which are in warranty have the better resell prices than the cars which are not covered under warranty.

Also we can see so many outliers in 'no warranty' categories. That pool is belongs to the vintage cars where prices are high but the car is not in the warranty.

### T-test

```{r results = F}
with_warranty<-subset(car_data,has_warranty == 'True')
without_warranty<-subset(car_data,has_warranty == 'False')
mean_price = mean(car_data$price_usd)
```

```{r results = F}
head(car_data)
```

T-test has been performed on has_warranty variable has two sub groups.

H0: Mean price of data is equal to the mean price of two subgroups (With_warranty and Without_warranty)

H1:Mean price of data is not equal to the mean price of two subgroups (With_warranty and Without_warranty)

```{r results = T}

Hypothesis_test_price_with_warranty = t.test(x=with_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_warranty


Hypothesis_test_price_without_warranty = t.test(x=without_warranty$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_warranty
```
The mean value of two sub categories has significant difference. Hence we are accepting alternate hypothesis.

## Does the odometer value have any impact on the car prices?

**Line Graph: Price(In USD) vs Odometer Value**

```{r results=T}
ggplot(data = car_data) +
    geom_smooth(mapping = aes(x = odometer_value, y = price_usd)) +
    scale_x_continuous(name="odometer_value", labels = scales::comma) +
        labs(x = 'odometer_value', y = 'price(in USD)') + labs(title = 'Line plot - Prices vs odometer values')
```

We can clearly see that as odometer value is increasing, car prices are going down.

**Violin Plot: Price(In USD) vs Odometer Value**

```{r results=T}
plot3 <- ggplot(car_data,aes(x = odometer_value,y = '',color = odometer_value)) +
        geom_violin(color="black", fill="pink") + geom_boxplot(width = .2,color="black", fill="violet") +
        labs(x = 'odometer_value') + labs(title = 'Violin Plot + Box Plot for Odometer values')
plot3
```


Violin plot, checking odometer distribution and box plot in the same graph. 


**Scatter plot with fitting line**

```{r}
updated_data = outlierKD2(car_data, odometer_value, TRUE, TRUE, TRUE, TRUE)
```
**Scatter Plot: Price(In USD) vs Odometer Value**

```{r}
ggplot(updated_data, aes(x=odometer_value, y=price_usd)) +
   geom_point()+
   geom_smooth(method=lm) +
   labs(title = 'scatter plot - car prices vs odometer values') +
   labs(x = 'odometer values(in KM)', y = 'price(in USD)') + scale_x_continuous(name='odometer values(in KM)', labels = scales::comma)
```

By removing outliers from odometer value, we are getting good relation for price vs odometer value.

### Correlation Plot

Correlation plot between the numerical features is considered

```{r include=FALSE}
car_data %>% select_if(is.numeric)->cars_numerical
```

```{r cor}
corrplot(cor(cars_numerical), method = 'number')
```

The above correlation plot shows the relation between all the numerical features and the price_usd.

Here, odometer_value has negative correlation with price(cc=-0.42). 

## Are the car prices dependent on the manufacturer or year of production?

**Based on Manufacturer**

Top 10 Brands and their Median price in USD.

```{r}
df_new <- aggregate( price_usd ~ manufacturer_name, car_data, median )
top_10_costy_brands <- df_new[df_new$price_usd %in% tail(sort(df_new$price_usd),10),]
top_10_costy_brands
```

```{r}
top_10_manufactuerer_avg_price=subset(car_data,manufacturer_name=='Acura'|manufacturer_name=="Buick"|manufacturer_name=="cadillac"|manufacturer_name=="Infiniti"|manufacturer_name=="Jaguar"|manufacturer_name=="Land Rover"| manufacturer_name=='Lexus'| manufacturer_name=="Mini"|manufacturer_name=="Porsche"|manufacturer_name=="Skoda")
```

**Boxplot - Price(In USD) vs Manufacturer**

```{r results=T}
plot_body <- ggplot(top_10_manufactuerer_avg_price, aes(x=manufacturer_name, y=price_usd)) + 
  geom_boxplot(color="black", fill="Yellow")+
  labs(x="Car_Manufacturer",y="Price(in USD)") + labs(title=" Top 10 Manufacturers and its Car Price") 
plot_body
```

### ANOVA Test

In this ANOVA test, we are checking that is there any significant difference in the mean price on the basis of car manufacturer.

H0: there is no difference in the mean prices of the cars based on manufacturer

H1: there is a difference in the mean prices of the cars based on manufacturer

```{r}
price_aov<-aov(price_usd ~ manufacturer_name, data=car_data)
price_aov
```

```{r}
xkabledply(price_aov, title = 'Anova test result impact of manufacturer_name on car price')
```

If p≤α, reject H0; otherwise, do not reject H0.

As we got p value less than α hence we reject the null hypothesis.

It means there is a significant difference in the mean price based on manufacturer.


**Based on year of Production**

Boxplot - Price(In USD) vs Year of Production

```{r results=T}
ggplot(data = car_data) +
    geom_smooth(color = 'red',mapping = aes(x = year_produced, y = price_usd)) + labs(x = 'Year of production', y = 'Price(in USD)') + 
    labs(title ='Year wise car price values')
```


As we can see that car prices of vintage cars is high. Also the resell price is high for latest cars.

```{r results=T}
plot_transmission <- ggplot(data = car_data) +
    geom_smooth(color = 'red',mapping = aes(x = year_produced, y = price_usd,linetype = transmission)) + 
    labs(title = 'Year wise car price values based on transmission type') + labs(x = 'Year of production', y = 'Price(in USD)')
plot_transmission
```

To check the Vintage category, mechanical are categorize as vintage and automatic cars are available from 1978. We are getting the similar results compared to the previous plot based on complete data.

### Chi Square Test

With the chi square test of independence, we are checking that resale car prices are dependent on the year of manufacture or not.

H0: Car prices and year of production are independent of each other.

H1: Car prices and year of production are dependent of each other.


```{r}
p_usd.intrv = cut(car_data$price_usd, c(0,10000,20000,30000,40000,50000))
year.intrv = cut(car_data$year_produced, c(1940,1950,1960,1970,1980,1990,2000,2010,2020))
lists <- list(price_intvl = as.character(p_usd.intrv),yr_interval = as.character(year.intrv))
df <- as.data.frame(do.call(cbind, lists))
conTable = table(df)
print(conTable)
```

```{r}
head(df,3)
```

```{r results=T}
chitest = chisq.test(conTable)
chitest
```


If p≤α, reject H0; otherwise, do not reject H0.

As we got p value less than 0.05 hance we are rejecting the null hypothesis.

It means prices and year of production are dependent of each other

## Does colour and body type have any impact on the resale prices of the cars?

**Boxplot - Price(In USD) vs Car color**

```{r results=T}
plot1 <- ggplot(car_data, aes(x=color, y=price_usd)) + 
  geom_boxplot(color="blue", fill="orange")+
  labs(x="Car Color",y="price_usd") + labs(title="Boxplot - Car Color and its Price (In USD)") 
plot1
```

### ANOVA Test

ANOVA is helpful for testing three or more variables.It is similar to multiple two-sample t-tests.The one-way ANOVA is used to determine whether there are any statistically significant differences between the means of three or more independent (unrelated) groups.

The null hypothesis states that the mean resale price in usd is equal among all color groups.

H0 : There is no difference in mean Prices based on color feature

H1 : There is difference in mean Prices based on color feature

Anova test for car color

```{r}
df_aov_1 = aov(price_usd ~  color , car_data)
summary(df_aov_1)
```

If p≤α, reject H0; otherwise, do not reject H0.

The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion:

At 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of color is different from each other.


**Based on Body Type**

**Boxplot - Price(In USD) vs Body Type**

```{r results=T}
plot_body <- ggplot(car_data, aes(x=body_type, y=price_usd)) + 
  geom_boxplot(color="black", fill="#F48FB1")+
  labs(x="body type",y="price(in USD)") + labs(title="Boxplot - Car Price distribution based on body type") 
plot_body
```

### ANOVA Test

The null hypothesis states that the mean resale price in usd is equal among all groups of car body type.

H0 : all means are equal

H1 : not all means are equal

Decide on the significance level
significance level is α=0.05

```{r}
df_aov_4 = aov(price_usd ~  body_type , car_data)
summary(df_aov_4)
```

If p≤α, reject H0; otherwise, do not reject H0.

The p-value is less than the specified significance level of 0.05; we reject null hypothesis. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion:

At 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of body type is different from each other.

## Does the number of photos have any impact on the car’s resale value?

Creating buckets for number of photos feature

```{r}

Photo_bucket <- within(car_data, {   
  Photo_bucket.cat <- NA # need to initialize variable
  Photo_bucket.cat[number_of_photos < 6] <- "0-5"
  Photo_bucket.cat[number_of_photos >= 6 & number_of_photos < 11] <- "6-10"
  Photo_bucket.cat[number_of_photos >= 11 & number_of_photos < 16] <- "11-15"
  Photo_bucket.cat[number_of_photos >= 16 & number_of_photos < 21] <- "16-20"
  Photo_bucket.cat[number_of_photos >= 21 & number_of_photos < 26] <- "21-25"
  Photo_bucket.cat[number_of_photos >= 26 & number_of_photos < 31] <- "26-30"
  Photo_bucket.cat[number_of_photos > 30] <- "more than 30"
   } )

Photo_bucket$Photo_bucket.cat <- factor(Photo_bucket$Photo_bucket.cat, levels= c("0-5","6-10","11-15","16-20","21-25","26-30","more than 30"))

```

**Boxplot - Price(In USD) vs Number of Photos**

```{r}

ggplot(Photo_bucket, aes(y = price_usd , x = Photo_bucket.cat)) + geom_boxplot(color="black", fill="#bc5090") + labs(title = 'Boxplot - impact of number of photos on car prices') + labs(x = 'Number of photos', y = 'Price(in USD)')

```

## Does drivetrain have any impact on the car’s resale value?


**Boxplot - Price(In USD) vs Drivetrain**

```{r results=T}
plot_warranty <- ggplot(car_data, aes(x=drivetrain, y=price_usd)) + 
  geom_boxplot(color="black", fill="#AF7AC5")+
  labs(x="drivetrain",y="price_usd") + labs(title="boxplot - Car Price distribution based on car drivetrain") 
plot_warranty
```

### ANOVA Test

H0: No difference in the mean price based on drivetrain.

H1: There is a difference in the mean price based on drivetrain.

```{r results=T}
cartrain_aov<-aov(price_usd ~ drivetrain, data=car_data)
cartrain_aov

xkabledply(cartrain_aov, title = 'Anova test result impact of drivetrain on car prices')
```

The p-value is less than the specified significance level of 0.05; we reject null hypothesis. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion:

At 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of body type is different from each other.

## Are the resale prices of the cars dependent on fuel and engine type? 

**Based on Engine Fuel**

**Boxplot- Price(In USD) vs Engine fuel**

```{r results=T}
plot1 <- ggplot(car_data, aes(x=engine_fuel, y=price_usd)) + 
  geom_boxplot(color="black", fill="green")+
  labs(x="engine_fuel",y="price(in USD)") + labs(title="boxplot - Car Price distribution based on engine_fuel") 
plot1
```

### ANOVA Test

The null hypothesis states that the mean resale price in usd is equal among all groups of engine fuel types.

Null Hypothesis         H0 : μ1=μ2=μ3=μ4=μ5=μ6

Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
significance level is alpha=0.05

```{r}
df_aov_2 = aov(price_usd~  engine_fuel , car_data)
summary(df_aov_2)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine fuel type is different from each other.

**Based on Engine Type**

*Density plot _ Price(In USD) vs Engine Type**

```{r results=T}
library(ggpubr)
xplot <- ggdensity(car_data, "price_usd", fill = "engine_type",
                   palette = "arc") + labs(title = 'density plot for car price based on engine type category') + labs(x = 'price(in USD)')
xplot
```

We can clearly separate out electric engine category from diesel and gasoline. most of the distribution is overlapped for diesel and gasoline and we can see the Pareto distribution in both the categories.

### ANOVA TEST

Setting the Hypothesis
The null hypothesis states that the mean resale price in usd is equal among all groups of engine types.

Null Hypothesis         H0 : μ1=μ2=μ3

Alternate Hypothesis    H1 : not all means are equal

Decide on the significance level
Significance level is alpha=0.05

```{r}
df_aov_3 = aov(price_usd~  engine_type , car_data)
summary(df_aov_3)
```

If p≤α, reject H0; otherwise, do not reject H0.
The p-value is less than the specified significance level of 0.05; we reject H0. The test results are statistically significant at the 5% level and provide very strong evidence against the null hypothesis.

Conclusion from anova test:
Again, we may conclude that at the 5% significance level, the data provides very strong evidence to conclude that at least one pair of group means of engine type is different from each other.


## Are the prices of the cars different based on the transmission type and engine capacity?

**Based on Transmission Type**

**Boxplot - Price(In USD) vs Transmission Type**

```{r results=T}
plot1 <- ggplot(car_data, aes(x=transmission, y=price_usd)) + 
  geom_boxplot(color="black", fill="orange")+
  labs(x="car_transmission",y="price_usd") + labs(title="boxplot - Car Price distribution based on transmission type") 
plot1
```
**Based on Engine Capacity**

**Line Graph - Price(In USD) vs Engine Capacity**

```{r results=T}
ggplot(data = car_data, aes(x = engine_capacity, y = price_usd)) +
    geom_smooth(color = 'yellow') +
    labs(title = 'Car price values based on Engine Capacity') + labs(x = 'Engine capacity', y = 'price(in USD)')
```


As engine capacity is going high, the prices are also increasing.



## Does unknown features have any impact on car prices?

Unknown features(feature0 to feature9)

### T-test on Feature 0

Is feature_0 impacting the average car price?

```{r}
with_feature_0<-subset(car_data,feature_0 == 'TRUE')
without_feature_0<-subset(car_data,feature_0 == 'FALSE')
```

```{r}
head(car_data,3)
```

```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature0 = t.test(x=with_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature0


Hypothesis_test_price_without_feature0 = t.test(x=without_feature_0$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature0
```

We got low price interval if feature0 is in the car. So probably its outdated feature.

### T-test on Feature 1

Is feature_1 impacting the average car price?

```{r}
with_feature_1<-subset(car_data,feature_1 == 'TRUE')
without_feature_1<-subset(car_data,feature_1 == 'FALSE')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature1 = t.test(x=with_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature1


Hypothesis_test_price_without_feature1 = t.test(x=without_feature_1$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature1
```

We got low price interval if feature0 is in the car.

### T-test on Feature 2

Is feature_2 impacting the average car price?

```{r}
with_feature_2<-subset(car_data,feature_2 == 'TRUE')
without_feature_2<-subset(car_data,feature_2 == 'FALSE')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature2 = t.test(x=with_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature2


Hypothesis_test_price_without_feature2 = t.test(x=without_feature_2$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature2
```

### T-test on Feature 3

Is feature_3 impacting the average car price?

```{r}
with_feature_3<-subset(car_data,feature_3 == 'TRUE')
without_feature_3<-subset(car_data,feature_3 == 'FALSE')
```


```{r results=T}

mean_price = mean(car_data$price_usd)
mean_price


Hypothesis_test_price_with_feature3 = t.test(x=with_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature3


Hypothesis_test_price_without_feature3 = t.test(x=without_feature_3$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature3
```

### T-test on Feature 4

Is feature_4 impacting the average car price?

```{r}
with_feature_4<-subset(car_data,feature_4 == 'TRUE')
without_feature_4<-subset(car_data,feature_4 == 'FALSE')
```

```{r results=T}

mean_price = mean(car_data$price_usd) 
mean_price


Hypothesis_test_price_with_feature4 = t.test(x=with_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature4


Hypothesis_test_price_without_feature4 = t.test(x=without_feature_4$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature4
```

### T-test on Feature 5

Is feature_5 impacting the average car price?

```{r}
with_feature_5<-subset(car_data,feature_5 == 'TRUE')
without_feature_5<-subset(car_data,feature_5 == 'FALSE')
```


```{r results=T}

mean_price = mean(car_data$price_usd) 
mean_price


Hypothesis_test_price_with_feature5 = t.test(x=with_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_with_feature5


Hypothesis_test_price_without_feature5 = t.test(x=without_feature_5$price_usd,mu = mean_price ,conf.level = 0.95) 
#default conf.level = 0.95
Hypothesis_test_price_without_feature5
```

